---
title: "What This Package Does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What This Package Does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL224753rich0142)
```

# Introduction

This is a package containing a variety of functions used in MATH 4753 in Fall of 2022.

#Functions

## First Function

This function is a negative binomial probability distribution using the parameters: y = quantile, r = size, p = probability.

```{r}
FALL224753rich0142::myNegBin(10,3,0.4)
```

## Second Function

This function creates a normal function graph with the shaded probability region using the parameters: mu = mean, sigma = standard deviation, a = upper bound of the region.

```{r}
FALL224753rich0142::myncurve(10,5,6)
```

## Third Function

This function gives the number of tickets to be sold regarding a plane's overbooking problem along with other values using the parameters: N = number of flight seats, gamma = overbooking probability, p = show probability.

```{r}
FALL224753rich0142::ntickets(200,0.02,0.95)
```

## Fourth Function

This function gives the binomial distribution using the central limit theorem using the parameters: n = sample, iter = iterations, p = probability.

```{r}
FALL224753rich0142::mycltb(4,10000,.3)
```

